Level-Set method on \texttt{p4est}

### 2014-08-29 paper/tex/levelset_method.tex
updated citation format

The work we present relies on the parallel octree library \texttt{p4est} \cite{burstedded:2011:p4est}. It is scalable implementation of the general octree structure in a massively parallel mpi environment. We limit our presentation of \texttt{p4est} to the relevant information for our application, for more details the reader is invited to read the original article \cite{burstedded:2011:p4est}.

>>>>

The work we present relies on the parallel octree library \texttt{p4est} \cite{Burstedde;Wilcox;Ghattas:11:p4est:-Scalable-Algo}. It is scalable implementation of the general octree structure in a massively parallel mpi environment. We limit our presentation of \texttt{p4est} to the relevant information for our application, for more details the reader is invited to read the original article \cite{Burstedde;Wilcox;Ghattas:11:p4est:-Scalable-Algo}.

### 2014-08-29 paper/tex/parallel_algorithms.tex
updated citation format

The reinitialization procedure transforms an arbitrary function into a signed distance function to its zero contour. One of the popular methods to achieve this results is to solve the reinitialization equation \ref{eq::reinitialization} \cite{Sussman:1994:levelsetincompressible, Min_Gibou:2007:Level_Set_Adaptive}. Other methods, such as the Fast Sweeping \cite{??} and the Fast Marching methods \cite{Sethian:1996:FMM, chopp:2001:fmm}, are based on the wave propagation nature of the reinitialization front and provide faster implementations of the reinitialization procedure in a serial environment. However, their parallelization is an involved process and we opt for solving the reinitialization equation.

We base our approach on Min and Gibou \cite{Min_Gibou:2007:Level_Set_Adaptive} and discretize the reinitialization equation as

@@

with $a^+=\max(a,0)$ and $a^-=\min(a,0)$. The one-sided derivatives $D^{+/-}_{x/y}\phi$ are discretized by second order accurate finite differences as explained by Min and Gibou in \cite{Min_Gibou:2007:Level_Set_Adaptive}. Following the presentation in \cite{Min_Gibou:2007:Level_Set_Adaptive} which incorporates the subcell resolution introduced by Russo and Smereka \cite{Russo_Smereka}, we include the initial position of the interface, given by $\phi^0$, in the computation of the one sided derivatives next to the interface in order to preserve the interface location. Finally, we choose a simple Euler step for the time discretization.

>>>>

The reinitialization procedure transforms an arbitrary function into a signed distance function to its zero contour. One of the popular methods to achieve this results is to solve the reinitialization equation \ref{eq::reinitialization} \cite{Sussman;Smereka;Osher:94:A-Level-Set-Approach, Min;Gibou:07:A-second-order-accur}. Other methods, such as the Fast Sweeping \cite{Zhao:04:A-Fast-Sweeping-Meth} and the Fast Marching methods \cite{Sethian:96:A-Fast-Marching-Leve, Chopp:01:Some-improvements-of}, are based on the wave propagation nature of the reinitialization front and provide faster implementations of the reinitialization procedure in a serial environment. However, their parallelization is an involved process and we opt for solving the reinitialization equation.

We base our approach on Min and Gibou \cite{Min;Gibou:07:A-second-order-accur} and discretize the reinitialization equation as

@@

with $a^+=\max(a,0)$ and $a^-=\min(a,0)$. The one-sided derivatives $D^{+/-}_{x/y}\phi$ are discretized by second order accurate finite differences as explained by Min and Gibou in \cite{Min;Gibou:07:A-second-order-accur}. Following the presentation in \cite{Min;Gibou:07:A-second-order-accur} which incorporates the subcell resolution introduced by Russo and Smereka \cite{Russo;Smereka:00:A-Remark-on-Computin}, we include the initial position of the interface, given by $\phi^0$, in the computation of the one sided derivatives next to the interface in order to preserve the interface location. Finally, we choose a simple Euler step for the time discretization.
